Design and Implementation of Probabilistic Programming Language Anglican

### 2017-02-06 paper/paper.tex
better language

In addition to the checkpoints, there are a few other special
forms ---  \texttt{store}, \texttt{retrieve}, \texttt{mem} ---
which modify program state. These forms are translated into
expressions involving calls of functions from the
\texttt{anglican.state} namespace. The \texttt{mem} form, which
implements memoization, deserves a more detailed explanation.
}{%
}%

>>>>

In addition to \texttt{sample} and \texttt{observe}, there are a few other special
forms ---  \texttt{store}, \texttt{retrieve}, \texttt{mem} ---
which modify program state. These forms are translated into
expressions involving calls of functions from the
\texttt{anglican.state} namespace. The \texttt{mem} form, which
implements memoization, deserves a more detailed explanation.
}{%
}%
